---
title: "Another quick rayshade"
author: "Nils Ratnaweera"
date: "2020-06-06T23:00:00+01:00"
categories: ["R"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, warning = FALSE, message = FALSE)
if(is.null(knitr::opts_knit$get("rmarkdown.pandoc.to"))){
  # setwd("content/post/2020_06_04_rayshader")
  eval = TRUE
} else{
  eval = FALSE
}

library(here)
library(knitr)
here_post <- here("content","post","2020_06_04_rayshader")
here_img <- here("static","img","2020_06_04_rayshader")

```



```{r}

library(raster)
library(sf)
library(tidyverse)

library(rayshader)
library(lazyraster)
library(geoviz)

```


```{r, eval = FALSE}
dem <- mapzen_dem(46.62874, 7.83063, 5)
```

```{r, eval = FALSE, echo = FALSE}
writeRaster(dem,file.path(here_post, "dem_saxeten.tif"))
```

The function returns a classical raster dataset in WGS84.
```{r, echo = FALSE}
dem <- raster(file.path(here_post, "dem_saxeten.tif"))
```


```{r}
plot(dem)
```

After downloading the landsat dataset, I can import it with the fuction `brick` from `raster`.

```{r}
# landsat <- brick("C:/Users/rata/Geodata/Landsat_25/LandsatMos25.tif")
landsat <- brick(file.path(here_post, "LandsatMos25.tif"))
crs(landsat) <- st_crs(21781)$proj4string
```

The two datasets, `dem` and `landsat` are in different coordinate systems and I need to reproject one into the other. If given the choice I prefer to work in a local, projected coordinate system and so will use `landsat`'s CRS (EPSG 21781).

```{r}
dem <- projectRaster(dem, crs = crs(landsat),method = "bilinear")
dem

# Round xmin / ymin to the next higher multiple of 25
xmn <- ceiling(extent(dem)@xmin/25)*25
ymn <- ceiling(extent(dem)@ymin/25)*25

# Round xmax / ymax to the next lower multiple of 25
xmx <- floor(extent(dem)@xmax/25)*25
ymx <- floor(extent(dem)@ymax/25)*25

# Create an empty raster with the right resolution and extent
dem2 <- raster(res = res(landsat),xmn = xmn, xmx = xmx, ymn = ymn, ymx = ymx,crs= crs(landsat))

# use values of dem to populate the new raster
dem2 <- raster::resample(dem,dem2)

dem2

dem_mat <- raster_to_matrix(dem2)

landsat <- crop(landsat, dem2)

plotRGB(landsat)


landsat_mat_list <- lapply(as.list(landsat), function(x){t(raster_to_matrix(x)/255)})
landsat_mat_list[[4]] <- t(raster_to_matrix(raster(nrows = nrow(landsat), ncols = ncol(landsat), ext = extent(landsat), resolution = raster::res(landsat), vals = 0.9)))

library(abind)
landsat_mat <- do.call(abind,list(landsat_mat_list,along = 3))

hill <- dem_mat %>%
  sphere_shade() 

rgl::clear3d()
zscale <- 20




hill <- add_overlay(hill, landsat_mat)


hill <- add_shadow(hillshade = hill, shadowmap = ambient_shade(dem_mat),max_darken = 0)

hill <- add_shadow(hillshade = hill, shadowmap = ray_shade(dem_mat), max_darken = 0.5)

rgl::clear3d()

plot_3d(hillshade = hill, heightmap = dem_mat, windowsize = c(1000, 600), zscale = zscale, theta = 160, zoom = 0.5, phi = 35, baseshape = "circle")

library(sf)
gpx <- st_read(file.path(here_post, "saxeten - rengglipass.gpx"),"track_points")
gpx_dfr <- as.data.frame(cbind(st_coordinates(gpx),gpx$ele))

geoviz::add_gps_to_rayshader(dem2, gpx_dfr$Y,gpx_dfr$X,alt = gpx_dfr$V3+100,zscale = zscale, 2, colour = "red",lightsaber = TRUE)

```




  
