# Swissboundries3D

```{r}
swissboundries <- "swissBOUNDARIES3D/swissBOUNDARIES3D.gpkg"
```

What layers are available in the geopackage?
```{r}
layers <- st_layers(swissboundries)

layers

layernames <- layers$name %>% set_names(.)

conn <- DBI::dbConnect(RSQLite::SQLite(),swissboundries)
```


What columns / fields do these layers have?
```{r}
imap(layernames, ~dbListFields(conn, .x))
```

What other tables are available in this Geopackage / SQLite Database?
```{r}
dbListTables(conn)

dbReadTable(conn, "gpkg_contents")
```


What are all the names of "Gemeinden"?
```{r}
dbGetQuery(conn, "SELECT DISTINCT NAME FROM hoheitsgebiet") %>%
  pull(NAME) %>%
  paste(collapse = ", ")
```

What are all the names of "Bezirke"?

```{r}
dbGetQuery(conn, "SELECT DISTINCT NAME FROM bezirksgebiet") %>%
  pull(NAME) %>%
  paste(collapse = ", ")
```

What are all the names of "Kantone"?

```{r}
dbGetQuery(conn, "SELECT DISTINCT NAME FROM kantonsgebiet") %>%
  pull(NAME) %>%
  paste(collapse = ", ")
```

Choose all "Gemeinden" which touch the Gemeinde Winterthur:
```{r}
winterthur_touches <- st_read(swissboundries, "hoheitsgebiet", query = "SELECT gemeinden.NAME AS name, gemeinden.geom AS geom FROM (SELECT * FROM hoheitsgebiet WHERE NAME = 'Winterthur') winterthur, hoheitsgebiet AS gemeinden WHERE st_touches(gemeinden.geom, winterthur.geom)")


ggplot(winterthur_touches) +
  geom_sf(aes(fill = name)) +
  geom_sf_label(aes(label = name)) +
  theme_void() +
  theme(legend.position = "none")

```

Choose all "Gemeinden" within the "Bezirk" of Surselva
```{r}
gemeinden_surselva <- st_read(swissboundries, query = "SELECT gemeinden.NAME as name, gemeinden.geom as geom FROM (SELECT * FROM 'bezirksgebiet' WHERE NAME = 'Surselva') surselva, 'hoheitsgebiet' as gemeinden WHERE st_contains(surselva.geom, gemeinden.geom)")

ggplot(gemeinden_surselva) +
  geom_sf(aes(fill = name)) +
  geom_sf_label(aes(label = name)) +
  theme_void() +
  theme(legend.position = "none")
```

